EpisoPass: Password Management based on \\ Episodic Memories

### 2016-04-13 paper/UIST2016/paper.tex
...

We propose a password manager \textit{EpisoPass} that supports
generating strong passwords based on the user's secret and unforgettable
episodic memories.
%
To use EpisoPass,
a user first collects question-answer pairs related to his episodic memory
and registers them with fake answers.
%
When a user wants to generate a password,
EpisoPass shows the questions and lists of possible answers and asks
the user to select correct ones.
Then EpisoPass generates a password by substituting characters of the
seed string based on the answer selections.
%
If only the user knows the correct answer,
% If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without using master passwords or secret devices that are
usually required on conventional password managers.
%
\end{abstract}

@@

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet.
%
Since short passwords are easily guessed by attackers, and
using the same password for different services is unsafe,
different long passwords should be used for different services.
However,
remembering many long passwords is almost impossible for ordinary people.
%
% According to Flor\^{e}ncio,
According to a research in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

@@

In spite of such attempts,
password-based authentication is still the most
convenient and strong method\cite{Bonnearu:ReplacePasswords},
and it is not supposed to get extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
for handling many strong passwords.
%
%{\PW}管理システムは
%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
%暗号化されたデータベースに{\PW}を格納するもの%
%
Most password managers remembers various passwords and
asks users to remember a single ``master password'' to access the database
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
%が多いが、サービス名をもとにマスター{\PW}を変換することによって
%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
%両者ともにマスター{\PW}の記憶は必須であり、
%マスター{\PW}を盗まれたり忘れたりする危険がある。
%
Password managers remember users' passwords and help them enter
passwords on various services.
Although password managers are useful,
users are usually forced to remember a ``master password''
or a special hardware device
for safely handle password managers, and
password managers usually run on limited devices.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
Memories in human brain is not uniform.
Some memories are very short-lived, and others are unforgettable.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily forget it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.
%

@@

Password generation on EpisoPass is performed through the following procedures:

\begin{enumerate}
\item A user registers many question texts related to the user's personal
secret episodic memories that the user never forgets,
and provide a correct answer and fake answers.

@@

\item EpisoPass shows the data to the user so that
the user can select an answer for each question.
Based on the user's selection,
EpisoPass substitutes characters in the seed string and generate
random-looking password candidate strings.
After selecting all right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a random-looking string
based on the selections.
When the user selects the right answer to all the questions,
the right password is calculated and shown at the top.

@@

In Figure \ref{web1},
``\textsf{Twitter123456}'' is provided as the seed string,
and according to the selections to the four questions,
the seed string is converted to a string
``\textsf{Lbasnln542202}'',
which can be used as the password for Twitter.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{figures/01e5507d090eb494a20bcbc47c86b1d2}
\caption{Selecting a different answer.}
\label{web1}
\end{figure}

@@

Capital letters in the seed string are substituted to capital letters in the password,
and digits in the seed string are substituted to digits,
so that generated passwords conforms to password character restrictions
sometimes required by the service.

@@

The second question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the last secret question is related to a more recent event
which the author thinks he can never forget.
All the questions are related to the author's episodic memories
that he thinks he never forgets, and nobody else knows which one of the
candidate answers is the right one.

@@

The strength of the generated password depends on the number of
questions and the secret level of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
but the strength of secret questions has not been studied enough.
%
% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
% 総当たりで{\PW}を生成するには
% 1億($10^8$)通りの試行が必要であり、
% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
% エントロピーは26.6ビットとなる。
%
When we use 10 secret questions with 20 answers and
there's no clue for the answer,
1 billion ($20^8$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
% {\SQ}と選択枝の数を10個程度用意すれば
% 通常の{\PW}と同程度の強度が期待できることになる。
%
It is almost the same entropy as using random 8-character English alphabets
as a password, in which case the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of secret questions is the key to using EpisoPass.
If the episodic memory is shared by someone else,
that person can easily answer the question and generate the
password just like the user.
%
The episode related to each question should not be known to other people,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first, but
when we try to remember experiences of old days,
we can recall many trivial episodes which are unforgettable but
not important to other people.
%
Old experiences like the following are candidates for
good questions used in EpisoPass.

@@

\item Memories of bad experience like blunders or defeat.

@@

Questions like ``Which one do you like best?'' should be avoided,
since some of the friends might know the user's taste.
Questions related to a episode which the user is proud of should also be
avoided, since the user might talk about the episode to somebody else.

@@

% 正答と同じカテゴリに属する単語を自動的にリストすることができれば
% 正答をもとにして簡単に偽答のリストを生成することができる。
In this way, fake answers can be easily listed
if it is possible to collect words which belong to the same
category as the right answer.
%
% ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
% 「同位語検索」と呼ばれ、
% Webのデータを利用した様々な同位語検索システムが提案されている%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval purposes
\cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
\cite{BooWa}% Boo!Wa!というサイトをやっている
\cite{Wang:2007:LSE:1441428.1442086}.% BooWa
%\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
We can use such techniques for getting similar names.

@@

Although everyone has to use authentication systems on the Net these days,
not everyone is familiar with handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is not intuitive and
people forget passwords frequently.
%
Using EpisoPass, people can use password-based systems without knowing
techniques for creating and remembering strong passwords.
They only have to provide
questions and answers based on secret episodic memories.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
used for the authentication.

\subsection{Periodic password update}

@@

In many services, users are adviced to define answers to secret questions like
``what is your mother's maiden name''
so that he can log into the service even when he forgets the password.
This kind of authentication is far less secure than simple password systems,
since it is fairly easy for attackers to get to the right answer.
The variation of system-provided questions are usually small, and
such challenge-response systems are considered to be
insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.

@@

Users don't have to be very careful about handling questions and answers.
They can even be put on a public place
if enough amount of questions and fake answers are provided.
%
Keeping secret is always a pain for many people including
the authors, but if the whole questions and answers used on EpisoPass
can be put on a public place,
handling it becomes very easy.
Usually we have to be very careful about handling
secret information like passwords, secret key for SSH, etc.
because they should not be copied or saved at unsafe places.
On the other hand,
we can save the EpisoPass data as a plain text file and put it at
any place without great care, since malicious person cannot calculate
passwords without having the owner's episodic memories.

@@

EpisoPass is just a string-conversion system and it does not
have any information on which candidate is the correct answer.
Also, it does not save any password information at any form, and
it is almost impossible to get the right password 
without having the episodic memory.

@@

Since the password is generated by the algorithm and the password
string is not kept on a computer in any form,
unexpected leak of the password is unlikely.
The user doesn't have to remember the string and
there is no chance he will reveal it to somebody
even when he is forced to tell the password.

@@

If, one of the passwords generated by EpisoPass is revealed
for some reason, other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a cracker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker can try all the answer combinations and find out
the answers to all the questions,
if questions and answers are also known by the attacker.
Once all the answers to the questions are known,
the attacker can freely generate all the passwords
generated by EpisoPass.

To prevent such troble, it is safer to keep all the questions and answers
in a secret place or
use many number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the 5th question shown in Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name and other similar names as candidate answers.

@@

Various types of image-based authentication systems have been proposed recently,
in the hope that images are easier to remember than text
because images are usually more directly linked to episodic memories.
However, on many systems,
users have to remember new information related to the images
used in the authentication process, or
perform special operation on the image, and
it is not much easier than using passwords.
%
Image-based authentication based on episodic memories might work
if anyone can prepare many images 
which are tightly linked to his episodic memories.
However, finding such images is usually not easy, and
image-only authentication systems would not take off
unless simple and effective technique is invented.
% [Malasym]

Even when a new ideal authentication method is invented,
replacing all the password-based systems should take very long, and
various password managers should be used until the ideal method
prevails in the whole world.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password manager only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass\cite{Stobert:2014:PMD:2683467.2683471}% Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' on an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password text with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
Since passwords for these services are remembered on the browser,
EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a problem for the authors, but
currently all the information for generating passswords is put on the Net
and no trouble has been found during the period.

Unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company nor supported by
famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to remove such obstacles in the future.

@@

We introduced a password management system EpisoPass
that converts a seed string into a password using the user's
episodic memories represented as a set of questions and answers
which can be solved only by the user.
%
Using EpisoPass with well-defined questions and answers,
a user can always retrieve various passwords without worrying about
remembering secret information.
%
We'll try to integrate the system with existing password-based
services, and finally hope to remove all the problems
derived from password-based authentication.

>>>>

We propose a password manager \textit{EpisoPass} that supports
generating strong passwords based on the user's secret and unforgettable
episodic memories.
%
To use EpisoPass,
a user first collects question-answer pairs related to his episodic memory
and registers them with fake answers.
%
When the user wants to generate a password,
EpisoPass shows the questions and lists of possible answers and asks
the user to select correct ones.
Then EpisoPass generates a password by substituting characters of the
seed string based on the selected answers.
%
If the user is the only person who knows the correct answer,
% If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without using master passwords or secret devices that are
usually required on conventional password managers.
%
\end{abstract}

@@

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet.
%
Since short passwords are easily guessed by attackers and
using the same password for different services is unsafe,
different long passwords should be used for different services.
However,
remembering many long passwords is almost impossible for ordinary humans.
%
% According to Flor\^{e}ncio,
According to a research in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

@@

However,
password-based authentication is still the most
convenient and strong method\cite{Bonnearu:ReplacePasswords},
and it is not supposed to get extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
Password managers remember users' passwords and help them enter
passwords on various services.
%
%{\PW}管理システムは
%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
%暗号化されたデータベースに{\PW}を格納するもの%
%
Most password managers can manage various passwords by
asking users to remember a single ``master password'' to access the database.
%
%が多いが、サービス名をもとにマスター{\PW}を変換することによって
%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
%両者ともにマスター{\PW}の記憶は必須であり、
%マスター{\PW}を盗まれたり忘れたりする危険がある。
%
Although password managers are useful,
users have to remember the master password
or use a special hardware device
for safely handle password managers, and
password managers usually run on limited devices.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
Memories in human brain are not uniform.
Some memories are very short-lived, and others are unforgettable.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.
%

@@

Password generation on EpisoPass is performed through the following steps:

\begin{enumerate}
\item A user registers many question texts related to the user's personal
secret episodic memories that the user never forgets,
and provides a correct answer and additional fake answers.

@@

\item EpisoPass shows the data to the user so that
the user can select the right answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates
random-looking password candidate strings.
After selecting all the right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a random-looking string
based on the selections.
When the user selects the right answers to all the questions,
the right password is calculated and shown at the top.

@@

In Figure \ref{web1},
``\textsf{Twitter123456}'' is provided as the seed string,
and according to the selections to the five questions,
the seed string is converted to a string
``\textsf{Lbasnln542202}'',
which can be used as the password for Twitter.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{figures/01e5507d090eb494a20bcbc47c86b1d2}
\caption{Selecting a different answer.}
\label{web11}
\end{figure}

@@

Capital letters in the seed string are substituted to capital letters in the password,
and digits in the seed string are substituted to digits,
so that generated passwords conforms to password character restrictions
sometimes requested by the service.

@@

The second question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the last question is related to a more recent event
which the author thinks he can never forget.
All the questions are related to the author's episodic memories
that he thinks he never forgets, and nobody else knows which one of the
candidate answers is the right one.

@@

The strength of the generated password depends on the number of
questions and the secret level of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321}, % どういうパスワードが強いか
but the strength of secret questions has not been studied enough.
%
% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
% 総当たりで{\PW}を生成するには
% 1億($10^8$)通りの試行が必要であり、
% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
% エントロピーは26.6ビットとなる。
%
When we use 10 secret questions with 20 answers and
there's no clue for the answer,
1 billion ($20^10$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
% {\SQ}と選択枝の数を10個程度用意すれば
% 通常の{\PW}と同程度の強度が期待できることになる。
%
It is almost the same entropy as using random 8-character English alphabets
as a password, in which case the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where online brute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of the questions is the key to using EpisoPass.
If the episode is shared by someone else,
that person can easily answer the question and generate the
password just like the user.
%
The episode related to each question should not be known to other people,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first, but
when we try to remember experiences of old days,
we can recall many trivial episodes which are unforgettable but
not important to other people.
%
Old experiences like the following are candidates for
good questions used in EpisoPass.

@@

\item Memories of bad experience like blunders or defeat.
(You don't tell it to anybody.)

@@

Questions like ``Which food do you like best?'' should be avoided,
since some of the friends might know the user's taste.
Questions related to an episode which the user is proud of should also be
avoided, since the user might talk about the episode to somebody else.

@@

% 正答と同じカテゴリに属する単語を自動的にリストすることができれば
% 正答をもとにして簡単に偽答のリストを生成することができる。
In this way, fake answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
% ひとつの単語もしくは単語の集合と同じカテゴリに属する単語を検索する手法は
% 「同位語検索」と呼ばれ、
% Webのデータを利用した様々な同位語検索システムが提案されている%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks%
\cite{Huang:2012:LFC:2426725.2426728}% 読んでないけど
\cite{BooWa}% Boo!Wa!というサイトをやっている
\cite{Wang:2007:LSE:1441428.1442086}.% BooWa
%\cite{大島裕明:2006-12-15}.% ライバルサーチ「やーやら」
We can use such techniques for getting similar names.

@@

Although everyone has to use authentication systems on the Internet these days,
not all the people are good at handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is not intuitive and
people forget passwords frequently.
%
Using EpisoPass, people can use password-based systems without knowing
techniques for creating and remembering strong passwords.
They only have to provide
questions and answers based on secret episodic memories.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
required for the service.

\subsection{Frequent password update}

@@

In many services, users are adviced to define answers to secret questions like
``what is your mother's maiden name''
so that he can log into the service even when he forgets the password.
This kind of authentication is far less secure than simple password systems,
since it is fairly easy for attackers to know the right answer.
The variation of system-provided questions are usually small, and
such challenge-response systems are considered to be
insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.

@@

Users don't have to be very careful about handling questions and answers.
They can even be put on a public place
if enough amount of questions and fake answers are provided.
%
Keeping secrets is always a pain for many people including
the authors, but if the whole questions and answers used on EpisoPass
can be put on a public place,
handling it becomes very easy.
Usually we have to be very careful about handling
secret information like passwords, secret key for SSH, etc.
because they should not be copied or saved at unsafe places.
On the other hand,
we can save the EpisoPass data as a plain text file and put it at
any place without great care, since malicious person cannot calculate
passwords without having the owner's episodic memories.

@@

EpisoPass is just a string-conversion system and it does not
have any information on which one is the correct answer.
Also, it does not save any password information in any form, and
it is almost impossible to get the right password 
without having the episodic memory.

@@

Since the password is generated by the algorithm and the password
string is not kept on a computer in any form,
unexpected leak of the password is unlikely.
The user doesn't have to remember the password string, and
there is no chance he will reveal it to somebody
even when he is forced to tell the password.

@@

If one of the passwords generated by EpisoPass is revealed
for some reason, other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a cracker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker can try all the answer combinations and find out
the answers to all the questions,
if questions and answers are also known by the attacker.
Once all the answers to the questions are known,
the attacker can freely generate all the passwords
generated with the same questions.

To prevent such troble, it is safer to keep all the questions and answers
in a secret place or
use sufficient number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the 5th question shown in Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name as well as other similar fake names.

@@

Various types of image-based authentication systems have been proposed recently,
in the hope that images are easier to remember than text
because images are usually more directly linked to episodic memories.
However, on many systems,
users have to remember new information related to the images
used in the authentication process, or
perform special operations on the image, and
it is not much easier than using passwords.
%
Image-based authentication based on episodic memories might work
if anyone can prepare many images 
that are tightly linked to his episodic memories.
However, finding such images is usually not easy, and
image-only authentication systems would not take off
until simple and effective technique is invented.
% [Malasym]

Even when a new ideal authentication method is invented,
replacing all the password-based systems should take very long, and
various password managers should be used until the ideal method
prevails in the whole world.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password managers only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' on an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password text with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
Since passwords for these services are remembered on the browser,
EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a pain for the authors, but
currently all the information for generating passswords is put on the cloud
and no trouble has been found during the period.

Unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company nor supported by
famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to eliminate such obstacles in the future.

@@

We introduced a password management system EpisoPass
that converts a seed string into a password using the user's
episodic memories represented as a set of questions and answers
which can be solved only by the user.
%
Using EpisoPass with well-defined questions and answers,
a user can always retrieve various passwords without worrying about
remembering secret information.
%
We'll try to integrate the system with existing password-based
services, and finally hope to eliminate all the problems
derived from password-based authentication.
